Towards a Pandemic-Scale Ancestral Recombination Graph of SARS-CoV-2

### 2023-04-11 paper.tex
Updates to figures and display items

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figures/mutational_spectra.pdf}
\caption{\label{fig:mutational_spectra}
Mutational spectrum of SARS-CoV-2 in
the wide ARG (sampled to mid-2021) compared to \cite{Yi2021-sc}.
Mutations are categorised by type (i.e., ancestral state $>$
derived state). The percentages of each mutation type from the wide ARG are
represented by blue bars and the percentages from Yi et al. by orange bars,
with the darker colours representing one direction (e.g., C$>$U) and the
lighter colours the reverse (e.g., U$>$C).}
\end{figure}

@@

% FIXME there's too much vspace between the rows here. Probably best to redo
% the formatting.
\begin{table} \centering
\begin{tabular}{l|c|c|c|c|c} \hline
\multicolumn{1}{c}{} & \multicolumn{3}{c}{\textbf{Jackson et al. (2021)}} &
\multicolumn{2}{c}{\textbf{sc2ts (wide ARG)}} \\ \hline
\textbf{Sample} &
\textbf{Group} & \textbf{Parents} & \thead{Breakpoint \\
interval(s)} &
\textbf{Parents} & \thead{Breakpoint \\ interval(s)} \\
\hline ALDP-11CF93B & A
    & \thead{B.1.177 \\ Alpha} & 21,255–21,613 & \thead{B.1.177.18 \\ Alpha} &
21,256–22,227 \\
    ALDP-125C4D7 & A & \thead{B.1.177 \\ Alpha} & 21,255–21,613 &
    \thead{B.1.177.18 \\ Alpha} & 21,256–22,227 \\
ALDP-130BB95 & A & \thead{B.1.177 \\ Alpha} & 21,255–21,613 &
    \thead{B.1.177.18 \\ Alpha} & 21,256–22,227 \\
LIVE-DFCFFE & A & \thead{B.1.177 \\ Alpha} & 18,998–20,294 &
    \thead{B.1.177.18 \\ Alpha} & 21,256–22,227 \\
QEUH-CCCB30 & B & \thead{B.1.36.28 \\ Alpha} & 6,528–6,953 &
    \thead{B.1.36 \\ Alpha} & 6,529–6,954 \\
QEUH-CD0F1F & B & \thead{B.1.36.28 \\ Alpha} & 6,528–6,953 &
    \thead{B.1.36 \\ Alpha} & 6,529–6,954 \\
MILK-1166F52 & C & \thead{Alpha \\ B.1.221.1} & 25,996–27,441 &
    \thead{Alpha \\ B.1.221} & 25,997–27,972 \\
MILK-11C95A6 & C & \thead{Alpha \\ B.1.221.1} & 25,996–27,441 &
    \thead{Alpha \\ B.1.221} & 25,997–27,972 \\
QEUH-109B25C & C & \thead{Alpha \\ B.1.221.1} & 25,996–27,441 &
    \thead{Alpha \\ B.1.221} & 25,997–27,972 \\
MILK-126FE1F & D & \thead{B.1.36.39 \\ Alpha} & 20,703–23,062 &
    \thead{B.1.36.39 \\ Alpha} & 22,445–23,063 \\
RAND-12671E1 & D & \thead{B.1.36.39 \\ Alpha} & 20,703–23,062 &
    \thead{B.1.36.39 \\ Alpha} & 22,445–23,063 \\
RAND-128FA33 & D & \thead{B.1.36.39 \\ Alpha} & 20,703–23,062 &
    \thead{B.1.36.39 \\ Alpha} & 22,445–23,063 \\
CAMC-CBA018 & n/a & \thead{B.1.177 \\ Alpha} & 20,389–21,254 &
    \thead{B.1.177 \\ Alpha} & 16,177–21,255 \\
CAMC-CB7AB3 & n/a & \thead{Alpha \\ B.1.177 \\ Alpha} & \thead{3,267–4,474 \\ 20,389–21,254} &
     \thead{Alpha \\ B.1.177 \\ Alpha} & \thead{3,268–5,388 \\ 16,177–21,255} \\
MILK-103C712 & n/a & \thead{B.1.177.17 \\ Alpha} & \thead{408–444 \\ 26,801–27,876} &
    n/a & n/a \\
QEUH-1067DEF & n/a & \thead{Alpha \\ B.1.177.9} & 10,523–10,869 &
    \thead{Alpha \\ B.1.177} & 7,729–10,870 \\ \hline
\end{tabular}
\caption{\label{tab:jackson}Recombinant sequences involving the Alpha (B.1.1.7)
variant reported by \cite{Jackson2021-ik} have recombinant
ancestry in the wide ARG. The breakpoint intervals and Pango lineage
assignments of the parents were taken from Table 2 (3SEQ results) of Jackson et
al., except the Pango lineage assignment of the parents of group B
recombinants, which were taken from Table 1 (motif-based results).}
\end{table}

@@

% \begin{tabular}{ll|clll}
% \toprule
% A Group (XA) & Jackson        & 21,255–21,613 & B.1.177/B.1.1.7 \\
%              & \texttt{sc2ts} &  21,256--22,227 & B.1.177.18/B.1.1.7 \\
% \midrule
% B Group & Jackson        &  6,528--6,954 & B.1.36/B.1.1.7  \\
%         & \texttt{sc2ts} &  6,529--6,954 & B.1.36/B.1.1.7  \\
% \midrule
% C Group & Jackson        &  25,997--27,972 &  B.1.1.7/B.1.221 \\
%         & \texttt{sc2ts} &  25,996--27,441 &  B.1.1.7/B.1.221 \\
% \midrule
% D Group & Jackson        &  21,575--23,063 &  B.1.36.17/B.1.1.7 \\
%         & \texttt{sc2ts} &  22,445--23,063 &  B.1.36.39/B.1.1.7 \\
% \midrule
% CAMC-CBA018 & Jackson        &  20,389--21,254 & B.1.177/B.1.1.7 \\
%             & \texttt{sc2ts} & 16,177--21,255 & B.1.177/B.1.1.7 \\
% \midrule
% \end{tabular}

@@

>>>>

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{figures/mutational_spectra.pdf}
\caption{\label{fig:mutational_spectra}
Mutational spectrum of SARS-CoV-2 in
the wide ARG (sampled to mid-2021) compared to \cite{Yi2021-sc}.
Mutations are categorised by type (i.e., ancestral state $>$
derived state). The percentages of each mutation type from the wide ARG are
represented by blue bars and the percentages from Yi et al. by orange bars,
with the darker colours representing one direction (e.g., C$>$U) and the
lighter colours the reverse (e.g., U$>$C).}
\end{figure}

@@

@@

\begin{table} \centering
\begin{tabular}{ll|clll}
\toprule
A Group (XA) & Jackson        & 21,255–21,613 & B.1.177/B.1.1.7 \\
             & \texttt{sc2ts} &  21,256--22,227 & B.1.177.18/B.1.1.7 \\
\midrule
B Group & Jackson        &  6,528--6,954 & B.1.36/B.1.1.7  \\
        & \texttt{sc2ts} &  6,529--6,954 & B.1.36/B.1.1.7  \\
\midrule
C Group & Jackson        &  25,997--27,972 &  B.1.1.7/B.1.221 \\
        & \texttt{sc2ts} &  25,996--27,441 &  B.1.1.7/B.1.221 \\
\midrule
D Group & Jackson        &  21,575--23,063 &  B.1.36.17/B.1.1.7 \\
        & \texttt{sc2ts} &  22,445--23,063 &  B.1.36.39/B.1.1.7 \\
\midrule
CAMC-CBA018 & Jackson        &  20,389--21,254 & B.1.177/B.1.1.7 \\
            & \texttt{sc2ts} & 16,177--21,255 & B.1.177/B.1.1.7 \\
\midrule
\end{tabular}
\caption{\label{tab:jackson}Comparison of recombination breakpoint intervals
and parent lineages for a subset of the data
reported by \cite{Jackson2021-ik}. [FIXME ADD MORE DETAIL]
More detailed results are given in
Table~\ref{tab:jackson_supplement}.}
\end{table}

@@

\section{Supplementary}

% FIXME there's too much vspace between the rows here. Probably best to redo
% the formatting.
\begin{table} \centering
\begin{tabular}{l|c|c|c|c|c} \hline
\multicolumn{1}{c}{} & \multicolumn{3}{c}{\textbf{Jackson et al. (2021)}} &
\multicolumn{2}{c}{\textbf{sc2ts (wide ARG)}} \\ \hline
\textbf{Sample} &
\textbf{Group} & \textbf{Parents} & \thead{Breakpoint \\
interval(s)} &
\textbf{Parents} & \thead{Breakpoint \\ interval(s)} \\
\hline ALDP-11CF93B & A
    & \thead{B.1.177 \\ Alpha} & 21,255–21,613 & \thead{B.1.177.18 \\ Alpha} &
21,256–22,227 \\
    ALDP-125C4D7 & A & \thead{B.1.177 \\ Alpha} & 21,255–21,613 &
    \thead{B.1.177.18 \\ Alpha} & 21,256–22,227 \\
ALDP-130BB95 & A & \thead{B.1.177 \\ Alpha} & 21,255–21,613 &
    \thead{B.1.177.18 \\ Alpha} & 21,256–22,227 \\
LIVE-DFCFFE & A & \thead{B.1.177 \\ Alpha} & 18,998–20,294 &
    \thead{B.1.177.18 \\ Alpha} & 21,256–22,227 \\
QEUH-CCCB30 & B & \thead{B.1.36.28 \\ Alpha} & 6,528–6,953 &
    \thead{B.1.36 \\ Alpha} & 6,529–6,954 \\
QEUH-CD0F1F & B & \thead{B.1.36.28 \\ Alpha} & 6,528–6,953 &
    \thead{B.1.36 \\ Alpha} & 6,529–6,954 \\
MILK-1166F52 & C & \thead{Alpha \\ B.1.221.1} & 25,996–27,441 &
    \thead{Alpha \\ B.1.221} & 25,997–27,972 \\
MILK-11C95A6 & C & \thead{Alpha \\ B.1.221.1} & 25,996–27,441 &
    \thead{Alpha \\ B.1.221} & 25,997–27,972 \\
QEUH-109B25C & C & \thead{Alpha \\ B.1.221.1} & 25,996–27,441 &
    \thead{Alpha \\ B.1.221} & 25,997–27,972 \\
MILK-126FE1F & D & \thead{B.1.36.39 \\ Alpha} & 20,703–23,062 &
    \thead{B.1.36.39 \\ Alpha} & 22,445–23,063 \\
RAND-12671E1 & D & \thead{B.1.36.39 \\ Alpha} & 20,703–23,062 &
    \thead{B.1.36.39 \\ Alpha} & 22,445–23,063 \\
RAND-128FA33 & D & \thead{B.1.36.39 \\ Alpha} & 20,703–23,062 &
    \thead{B.1.36.39 \\ Alpha} & 22,445–23,063 \\
CAMC-CBA018 & n/a & \thead{B.1.177 \\ Alpha} & 20,389–21,254 &
    \thead{B.1.177 \\ Alpha} & 16,177–21,255 \\
CAMC-CB7AB3 & n/a & \thead{Alpha \\ B.1.177 \\ Alpha} & \thead{3,267–4,474 \\ 20,389–21,254} &
     \thead{Alpha \\ B.1.177 \\ Alpha} & \thead{3,268–5,388 \\ 16,177–21,255} \\
MILK-103C712 & n/a & \thead{B.1.177.17 \\ Alpha} & \thead{408–444 \\ 26,801–27,876} &
    n/a & n/a \\
QEUH-1067DEF & n/a & \thead{Alpha \\ B.1.177.9} & 10,523–10,869 &
    \thead{Alpha \\ B.1.177} & 7,729–10,870 \\ \hline
\end{tabular}
\caption{\label{tab:jackson_supplement}Recombinant sequences involving the Alpha (B.1.1.7)
variant reported by \cite{Jackson2021-ik} have recombinant
ancestry in the wide ARG. The breakpoint intervals and Pango lineage
assignments of the parents were taken from Table 2 (3SEQ results) of Jackson et
al., except the Pango lineage assignment of the parents of group B
recombinants, which were taken from Table 1 (motif-based results).}
\end{table}
